Prelim Outline

### 2019-07-30 outline.tex
edited + shortened draft. have 1.5 pages for references now.

\section{Introduction}
\begin{itemize}
\item Systematically developing model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for strongly correlated electron systems is a pressing problem in modern condensed matter physics.

\item The necessity for non-perturbative, many-body models in describing the low-lying excited states of strongly correlated electron systems poses a difficult challenge when developing effective theories for real world systems.

\item Common approaches to building suitable model Hamiltonians for strongly correlated materials involve using single particle theories like density functional theory (DFT).

\item We propose using a DMD procedure to develop accurate many-body effective theories for single (SLG) and bi-layer graphene (BLG) systems as a step towards building a many-body model for twisted bilayer graphene (TBLG).
\end{itemize}

\section{Methods}
\begin{enumerate}
\item Density matrix downfolding
\begin{itemize}
\item We begin by defining what we mean by a low-energy effective Hamiltonian and downfolding.

\item The key insight of DMD is that the Hamiltonian downfolding problem can be mapped onto an equivalent linear regression problem.

@@

\item Generally, one cannot sample the true low-energy subspace and an approximate subspace $\mathcal{LE}^\prime$ is sampled.

@@

\item Typically, candidate operators are written in second quantized form, and an appropriate single particle basis to express these operators must be constructed.

@@

\item We take advantage of the variational nature of FN-DMC to sample the low-energy states necessary for DMD.
\end{itemize}
\end{enumerate}

@@

\paragraph{CuO: Introduction} As a first step towards developing accurate models for extended systems like solids using DMD, we constructed a many-body effective model for the CuO molecule which accurately describes the eigenstates and spectra seen in experiment up to 2eV above the ground state.

\paragraph{CuO: Methods} In order to fit a model using DMD we had to construct a low energy space (LES), choose a sampling scheme for states within the LES resulting in our sample space (SS), develop a basis which can accurately describe variations within the LES, identify and select descriptors built out of these basis elements, and appropriately fit the data from our SS onto our selected descriptors.

\paragraph{CuO: Results and Discussion} The resultant model from our analysis accurately describes the various eigenstates as measured in experiment up to 2eV, and is quantitatively and qualitatively more accurate than competing methods like density functional theory.

\paragraph{Hubbard: Preliminary results} Our preliminary calculations on the 2x2 half-filled 1-band Hubbard model map out the limiting behavior in the U-T model space by investigating the effectiveness of the single descriptor models. \textcolor{red}{Will be changed based on how far along we get with preliminary results.}

\section{Proposed work}
\begin{itemize}
\item My proposed plan involves building a sequence of model Hamiltonians for increasing complicated systems using DMD, working towards an accurate many-body model for TBLG.

\item The first system I will develop a model for is the benzene molecule.

\item While relatively simple, this molecule shares many similarities with and forms the basic unit of SLG.

\item As such, developing a model for benzene will help me become familiar with model fitting for 2-D carbon based systems.

@@

@@

\item Note also that a model for benzene has already been developed using DMD.

\item This makes benzene a useful system not only for my personal learning, but as a benchmarking system for new methods like CVMC which have been developed recently.

\item The model I am interested in working on will be an extension of a previous model developed for SLG using DMD.

\item I will extend the previous model by introducing long range density-density interactions into the effective theory.

\item The candidate model I anticipate to work with is an extended Hubbard model of the form.

\item CVMC will be used to sample the low-energy wave functions necessary to fit the model.

\item The last systems I will develop models for are AA and AB stacked BLG.

\item Being the simplest BLG configuration, these models will form a starting point for a more thorough development of models for TBLG.

\item I will again use CVMC to generate the low-energy wave functions for the model regression.

\item The final four models can be used to investigate the transferrability of model parameters between these different carbon-based systems.

\item I will conclude by briefly discussing potential avenues of further study in using DMD to develop model Hamiltonians for TBLG.

\end{itemize}
\section{Proposed timeline}
\textit{Do this after proposed work nailed down}.

>>>>

\section{Introduction}
\begin{itemize}
\item Developing model Hamiltonians for realistic materials is a fundamental problem in modern condensed matter physics.

\item Yet unresolved is a paradigm for building many-body model Hamiltonians which can describe realistic systems.

\item Common approaches to building many-body theories for real materials involve density functional theory (DFT).

\item I propose using a quantum Monte Carlo (QMC) density matrix downfolding (DMD) procedure to develop accurate many-body model Hamiltonians for single (SLG) and bi-layer (BLG) graphene systems.
\end{itemize}

\section{Methods}
\begin{enumerate}
\item Density matrix downfolding
\begin{itemize}
\item I begin by defining what a low-energy effective Hamiltonian and downfolding are.

\item The key insight of DMD is that the Hamiltonian downfolding problem can be mapped onto a linear regression problem.

@@

@@

@@

\item One can take advantage of the variational nature of FN-DMC to sample the low-energy states necessary for DMD.
\end{itemize}
\end{enumerate}

@@

\begin{enumerate}
\item Intro (no subsection)
\begin{itemize}
\item As a first step towards developing accurate models for extended systems like solids using DMD, I constructed a many-body effective model for the CuO molecule by downfolding (1) under a Born-Oppenheimer approximation with fixed bond length $r_e$ = 1.725\r{A}.
\end{itemize}

\item Sampling low-energy states
\begin{itemize}

\item For the CuO molecule, low-energy states were generated by
using FN-DMC projected multi-Slater-Jastrow (MSJ) trial wave functions.

\item The determinants were constructed from the orbitals of independent symmetry-targeted unrestricted Kohn Sham (UKS) calculations.

\item A shell sampling scheme was used to sample states from the selected approximate low-energy space.

\item The final sampled MSJ states were projected using FN-DMC to generate our low-energy states.
\end{itemize}

\item Selecting candidate descriptors 
\begin{itemize}
\item We selected the following set of 1- and 2-body operators to construct our candidate descriptors based on our understanding of the low-energy excitations of the CuO molecule and our sampled states

\item The parantheses of \textbf{eqref} contain the full set of symmetry allowed 1-body operators within the Cu 3d, 4s and O 2p space
\end{itemize}

\item Fitting the effective Hamiltonian 
\begin{itemize}
\item {A direct attempt at fitting all eleven terms in \textbf{eqref} leads to a high goodness of fit but unexpectedly large coefficients for the fit model.}

\item A principal component regression (PCR) was used to alleviate this multicollinearity and fit the effective theory.

\item From the PCA, the nine highest ranked PCs were selected to use in the PCR.

\item {The model fit to these nine PCs maintains an excellent goodness of fit without serious multicollinearity.}
\end{itemize}

\item Solutions of effective Hamiltonian
\begin{itemize}
\item Solutions of our effective Hamiltonian are obtained by exact diagonalization.

\item The model is solved by exact diagonalization, and the solutions
agree well with experimental spectra and state assignments.

\item The model states also agree with recent theoretical calculations like UKS and CCSD(T).
\end{itemize}
\end{enumerate}

\section{Proposed work}
\begin{itemize}
\item My proposed plan involves building a sequence of model Hamiltonians for increasingly complicated graphene-like systems using QMC DMD, ending with BLG.

\item The first system I will develop a model for is the benzene molecule, shown in Figure 2a.

@@

\item In particular, I will work to extend a previous on-site Hubbard model developed for SLG by including long range density-density interactions.

\item The last systems I will develop models for are AA and AB stacked BLG, shown in Figure 2b.

@@

\item I will use a multi-Slater-Jastrow (MSJ) parameterization in the CVMC sampling for each system.

\item Apart from their individual value, the four models can be used to investigate the transferrability of model parameters between these different carbon-based systems.

\item Further, my calculations will help mature methods like CVMC for further usage on strongly correlated systems.

\item Lastly, my calculations will lay the groundwork for model development for the strongly correlated TBLG system using DMD.
\end{itemize}
\section{Proposed timeline}
